Improving Usability of Remote Access to Sensitive Data

### 2014-07-28 ccsw14/paper.tex
fixed bibliography

Current state-of-the-art systems developed for the purpose of enabling access to
these types of data use remotely accessed machines, which can then be used by
researchers without the need for travel to conduct their analysis. But beyond
this apparent convenience, rules for using such systems are often highly
restrictive, with researchers limited to using predefined software environments,
and being subject to strict auditing requirements for all software and data that
is uploaded to these software environments.

@@

Systems that enable supervised and audited computational research of sensitive
data date back at least as far as the 1990s, when a Census Research Data Center
was opened in Boston.  Since the opening of this initial office, the U.S.
federal government has established several Research Data Centers (RDCs) across
the country to enable researchers access to unpublished Census data for the
purpose of conducting research that could provide beneficial guidance to public
policy.

@@

More recently, the Centers for Medicare and Medicaid Services began providing
Medicare and Medicaid data using the CMS Virtual Research Data Center (VRDC) in
2013.  VRDC provides a more flexible model by allowing researchers to remotely
access desktop environments provided by a cloud infrastructure.  This model
relieves researchers of the need to travel to a physical location, and also
avoids the security risk of researchers having to receive and safeguard physical
copies of the data while they are conducting their research, as was formerly the
case.

@@

The virtual machine infrastructure that underlies the Data Capsules system is
trusted and assumed to be well implemented.  While this assumption may be
somewhat controversial, we note its use in prior work~\cite{capsules}, and also
note the existence of microkernels such as seL4 and OKL4~\cite{sel4, OKL4},
which serve as a proof of concept that it is possible to create a lightweight
hypervisor with a reasonable degree of trustworthiness based in formal proofs
of correctness.  However, the development of such a hypervisor lies outside the
scope of this paper.

@@

Because limiting access to only a small set of servers eliminates access to
public DNS servers, for our prototype we configured the \texttt{/etc/hosts} file
on VM images to allow them to resolve the server domain names when in secure
mode.  More elegant solutions could be achieved by allowing access to a
custom purpose-built DNS server, or by using solutions like cloud-init, which is
available for Linux based virtual machines.

>>>>

The current state-of-the-art \cite{vrdc} in systems developed for the purpose
of enabling access to these types of data use remotely accessed machines, which
can then be used by researchers without the need for travel to conduct their
analysis. But beyond this apparent convenience, rules for using such systems
are often highly restrictive, with researchers limited to using predefined
software environments, and being subject to strict auditing requirements for
all software and data that is uploaded to these software environments.

@@

Systems that enable supervised and audited computational research of sensitive
data date back at least as far as the 1990s, when a Census Research Data Center
was opened in Boston.  Since the opening of this initial office, the U.S.
federal government has established several Research Data Centers (RDCs)
\cite{census-rdc} across the country to enable researchers access to
unpublished Census data for the purpose of conducting research that could
provide beneficial guidance to public policy.

@@

More recently, the Centers for Medicare and Medicaid Services began providing
Medicare and Medicaid data using the CMS Virtual Research Data Center (VRDC) in
2013 \cite{vrdc}.  VRDC provides a more flexible model by allowing researchers
to remotely access desktop environments provided by a cloud infrastructure.
This model relieves researchers of the need to travel to a physical location,
and also avoids the security risk of researchers having to receive and
safeguard physical copies of the data while they are conducting their research,
as was formerly the case.

@@

The virtual machine infrastructure that underlies the Data Capsules system is
trusted and assumed to be well implemented.  While this assumption may be
somewhat controversial, we note its use in prior work~\cite{capsules-borders},
and also note the existence of microkernels such as seL4 and OKL4~\cite{sel4,
sel4-secure, OKL4}, which serve as a proof of concept that it is possible to
create a lightweight hypervisor with a reasonable degree of trustworthiness
based in formal proofs of correctness.  However, the development of such a
hypervisor lies outside the scope of this paper.

@@

Because limiting access to only a small set of servers eliminates access to
public DNS servers, for our prototype we configured the \texttt{/etc/hosts}
file on VM images to allow them to resolve the server domain names when in
secure mode.  More elegant solutions could be achieved by allowing access to a
custom purpose-built DNS server, or by using solutions like
cloud-init\cite{cloudinit}, which is available for Ubuntu-based virtual
machines.
